%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Platform Engineering Director} % Job title
    {Slalom} % Organization
    {Chicago, IL} % Location
    {January 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed the careers of 15+ engineers, shaping meaningful work while supporting regional leadership and capability expansion.}
      \end{cvitems}
    }

  \cventry
    {Commodities Trading Firm (Project Lead)} % Client detail
    {} % Skip for subentry
    {} % Skip for subentry
    {} % Skip for subentry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed multi-functional team to design and deliver secure cloud automation and self-service provisioning of architectural patterns for large language model development and operations (LLMOps).}
        \item {Designed a self-service platform for requests, approvals, and deployments of pre-approved patterns, with integrations to a configuration management database to support ITSM and asset tracking, leading to a 10\% reduction in cloud costs following decommission of unmanaged resources.}
        \item {Led threat assessment and table top exercises for GenAI security hardening and vulnerability management.}
        \item {Technologies: Azure API Management, Azure Firewall, Azure OpenAI, Azure CosmosDB, Azure SQL, Azure Monitor, ServiceNow, Terraform, GitHub Actions, Bash.}
      \end{cvitems}
    }

  \cventry
    {Health and Benefits Financial Institution (Platform Lead)} % Client detail
    {} % Skip for subentry
    {} % Skip for subentry
    {} % Skip for subentry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed modern platform architecture definition and delivery to support consumer driven benefits management via a greenfield, white-label, multi-tenant SaaS platform.}
        \item {Delivered Azure landing zone (multi-region hub-and-spoke), and developer portal to enable self-service management of service onboarding for 3 architectural patterns.}
        \item {Defined overall approach for eventual multi-cloud strategy to support GCP architecture.}
        \item {Technologies: Azure Front Door, Azure API Management, Azure Firewall, Azure CosmosDB, Azure SQL, Azure Functions, Datadog, Terraform, Azure DevOps, Backstage.io, React, .NET Core, Bash.}
      \end{cvitems}
    }

  \cventry
    {Freight Brokerage and Logistics Firm (Platform Lead)} % Client detail
    {} % Skip for subentry
    {} % Skip for subentry
    {} % Skip for subentry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a multi-level architecture team spanning product architecture and engineering operations to modernize legacy logistics platforms supporting a multi‑billion‑dollar business.}
        \item {Defined cases using a Strangler approach to maintain legacy systems and modernized systems in parallel, gathering feedback from users to define new features and functionality.}
        \item {Led domain-based intake model with up to 4 parallel streams to define the engineering needs and architecture of individual domains within a large enterprise application, delivering common patterns across three-tier, data streaming, and desktop application architectures.}
        \item {Technologies: Azure Front Door, Azure API Management, Azure Firewall, Azure SQL, Azure AKS, Rancher, Argo CD, Confluent Kafka, Elasticsearch, DataDog, Terraform, Azure DevOps, React, .NET Core, Bash.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Platform Engineering Senior Principal} % Job title
    {Slalom} % Organization
    {Chicago, IL} % Location
    {January 2020 - January 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed a team of 6+, championing practice development and career growth; promoted 2 engineers into senior contributor roles, and 1 into a leadership role.}
      \end{cvitems}
    }

  \cventry
    {Major Commercial Airline (Platform Lead)} % Client detail
    {} % Skip for subentry
    {} % Skip for subentry
    {} % Skip for subentry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led platform and site reliability engineering for delivery of a machine learning operations (MLOps) platform to provide personalized travel recommendations, improve baggage processing, and automate COVID-19 testing submission.}
        \item {Designed CI/CD pipelines to accelerate manual machine learning tasks like data preparation, model creation, and model deployment, leading to 5 models deployed within the first 6 months of the program.}
        \item {Delivered multi-region active/active runtime architectural design to enable near real-time recovery point (RPO) and recovery time (RTO) objectives for critical services.}
        \item {Technologies: AWS SageMaker, AWS RDS, AWS EKS, Rancher, Argo CD, Argo Workflows, Apache Spark, Prometheus, Grafana, Terraform, GitHub Actions, Python, Bash.}
      \end{cvitems}
    }

  \cventry
    {United States Federal Agency (Platform Lead)} % Client detail
    {} % Skip for subentry
    {} % Skip for subentry
    {} % Skip for subentry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led platform and security engineering for a massive (150+ consultants), multi-vendor federal program to provide scaled operational engineering support for on-going development of verification systems that support millions of transactions every year.}
        \item {Transitioned 8 legacy systems (6 internal and 2 public-facing) to modern pipeline automation and cloud hosting, improving deployment frequency (average of 50 - 100 production commitments per week) and system reliability (10x increase in mean time between failures).}
        \item {Delivered FinOps architecture and automation to identify areas contributing to high technical spend, leading to reduced AWS costs of approximately 20\% by 2020.}
        \item {Technologies: AWS EKS, AWS ECS, AWS Lambda, AWS API Gateway, Apigee API Management, Akamai CDN, New Relic, Splunk, Terraform, Packer, Ansible, Jenkins, GitHub Actions, Java, React, Bash.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Platform Engineering Principal} % Job title
    {Slalom} % Organization
    {Chicago, IL} % Location
    {February 2019 - January 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Defined SRE practice for operations-oriented engineering engagements, helping launch a new portfolio of opportunities for the firm to act as a managed service provider.}
      \end{cvitems}
    }

  \cventry
    {Mortgage Loan Bank (Platform Lead)} % Client detail
    {} % Skip for subentry
    {} % Skip for subentry
    {} % Skip for subentry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Defined and delivered modern pipeline (Azure DevOps) and runtime architectures (AWS) to rewrite and replatform an eBanking portal and loan underwriting platform responsible for receiving, validating, and processing loan requests from hundreds of member financial institutions.}
        \item {Led engineering approach across people (culture, learning), process (operating model), and technology (modern pipeline and runtime architecture) following development that increased deployment frequency from monthly to daily and reduced change failure rate by over 50\%.}
        \item {Delivered a suite of Terraform modules and Azure DevOps templates for over 10 reference patterns to reduce new services onboarding time from weeks to hours.}
        \item {Technologies: AWS API Gateway, AWS CloudFront, AWS Lambda, Terraform, Ansible, Azure DevOps, .NET Core, Angular, Bash.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Site Reliability Engineer} % Job title
    {Seismic Software} % Organization
    {Chicago, IL} % Location
    {April 2018 - February 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed cloud infrastructure for both greenfield and newly acquired services in a multi-cloud architecture across AWS, Azure, GCP, and IBM.}
        \item {Reverse engineered cloud infrastructure to Terraform definitions for infrastructure as code (IaC) management, improving deployment consistency and reducing manual errors.}
        \item {Led microservices migration from monolithic architecture into Kubernetes and serverless hosting for core revenue line services, enabling faster development cycles and improved scalability.}
        \item {Worked hands-on with teams to modernize workflows and accelerate speed-to-market by defining and automating Day 1 and Day 2 operations for software and data engineering.}
        \item {Technologies: AWS, Azure, GCP, IBM Cloud, Kubernetes, Helm, Terraform, Packer, Ansible, Jenkins, Python, Bash.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Skytap} % Organization
    {Seattle, WA} % Location
    {July 2017 - April 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed a Ruby on Rails REST API to enable cloud resource operations for enterprise customers needing to migrate and manage legacy AIX and IBM i (AS/400) workloads alongside conventional x86 workloads in the cloud.}
        \item {Led effort to migrate REST services from virtualized hosting to Kubernetes, leading to significant reduction in operational costs due to cluster bin packing.}
        \item {Delivered observability for REST services, including telemetry instrumentation and dashboards, to improve incident response and system reliability.}
        \item {Answered pager calls and resolved incidents as part of a 24/7 on-call rotation, ensuring high availability and reliability of all production services.}
        \item {Technologies: Kubernetes, VMware vSphere, Jenkins, NGINX, InfluxDB, Grafana, Ruby, Golang, Bash.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Skytap} % Organization
    {Seattle, WA} % Location
    {June 2015 - July 2017} % Date(s)
    {}

%---------------------------------------------------------
\end{cventries}
